\documentclass{article}
\usepackage[at]{easylist}
\usepackage[margin=1in]{geometry}

\begin{document}

\section*{Detailed Requirements (baselined version)}

\begin{easylist}[articletoc]

  @ The web service shall display a home page for the user when the user accesses the service.
  @@ If the user is not logged in, the web service shall display an Intro page allowing the user to (1) login and (2) create an account. 
  @@ If the user is logged in, the web service shall display a home page with the following greeting message: ``Welcome!''
  @ The Intro page shall present an account creation form allowing the user to create an account.
  @@ \label{form_fields} The account creation form shall contain the following form fields in the order given:
  @@@ Name
  @@@ Email
  @@@ Username
  @@@ Password
  @@ These form fields shall be subject to the data requirements in Section \ref{data_reqs_form_fields}.
  @@ The account creation form shall include a ``Sign Up'' button below the form fields.
  @@ When the user clicks the ``Sign Up'' button, the service shall validate the form field values.
  @@@ The service shall determine whether the form field values are consistent with the data requirements in Section \ref{data_reqs_form_fields}.
  @@@ If any form field value is inconsistent with the data requirements, the service shall display a warning message to the user and prevent the user from creating an account.
  @@ If validation is successful, the service shall create an account for the user.
  @@@ The service shall convert the case-insensitive form field values as specified in Section \ref{data_reqs_form_fields} to lowercase.
  @@@ The service shall insert the form field values in the database as a new `user` document.
  @@ The service shall prevent duplicate accounts.
  @@@ The service shall determine if another account exists which has the same username as the username value supplied by the user.
  @@@@ If there is a match, the service shall display a warning and prevent the user from creating an account.
  @@@ The service shall determine if another account exists which has the same email as the email value supplied by the user.
  @@@@ If there is a match, the service shall display a warning and prevent the user from creating an account.
  @ The Intro page shall present a login form allowing the user to login to the service.
  @@ The login form shall contain the following form fields in the order given:
  @@@ Username
  @@@ Password
  @@ The user shall display a button labelled ``Login'' below the form fields.
  @@@ When the user clicks the ``Login'' button, the service shall convert the username value that the user supplied to lowercase.
  @@@ The service shall then determine whether there exists an account with the lowercase username and password that the user has supplied.
  @@@ If there does not exist an account, the service shall display an ``Invalid credentials'' warning to the user and prevent the user from logging in.
  @@@ If there exists an account, the service shall display the user's account home page (see Section \ref{data_reqs}).
  @ \label{data_reqs} Data Requirements.
  @@ \label{data_reqs_form_fields} The service shall enforce the following form field requirements.
  @@@ Name
  @@@@ The name value shall be between 1 character and 30 characters in length, inclusive.
  @@@@ The name value shall be case-sensitive.
  @@@ Email
  @@@@ The email value shall be unique across all accounts.
  @@@@ The email value shall be case-insensitive.
  @@@@ The email value shall adhere to the email address requirements as specified by the client-side JavaScript framework.
  @@@ Username
  @@@@ The username value shall be unique across all accounts.
  @@@@ The username value shall be case-insensitive.
  @@@@ The username value shall be between 3 characters and 15 characters in length, inclusive.
  @@@ Password
  @@@@ The password value shall be between 6 characters and 12 characters in length, inclusive.
  @@@@ The password value shall contain only alphanumeric characters.
  @@@@ The password value shall be sensitive.
  @@ The service shall store its data in a MongoDB database.
  @@@ The database shall have a \texttt{users} collection to store user data.
  @@@ The \texttt{users} collection shall have fields for storing the respective form field values in Section \ref{form_fields}.
  @@@ The database shall have a unique index on each form field specified as unique in Section \ref{data_reqs_form_fields}.

\end{easylist}

\end{document}