\documentclass{article}
\usepackage[at]{easylist}
\usepackage[margin=1in]{geometry}

\begin{document}

\section*{Detailed Requirements (baselined version)}

\begin{easylist}[articletoc]
@ When the user clicks a bucket name in the bucket list, the user shall be directed to said bucket's page. This bucket name shall hereafter be referred to as the \textit{bucket name}, and this page shall hereafter be referred to as the \textit{bucket page}.
@@ The bucket page shall display a \textit{back button} labeled ``Back'' at the top of the page.
@@@ When the user clicks the back button, the user shall be directed to the home page.
@@ The bucket page shall display a \textit{bucket title} immediately below the back button.
@@@ The text of the bucket title shall be ``$\ll$bucket name$\gg$ Bucket.''
@@ The bucket page shall display a \textit{drip list} immediately below the bucket title.
@@@ \label{drip-list-belonging}A drip shall belong in the drip list if said drip's \texttt{bucketNames} array contains the bucket name. This containment check shall be performed in a case-sensitive manner.
@@@ Drips belonging in the drip list as per Section~\ref{drip-list-belonging} shall be listed in reverse chronological order\footnote{That is, the more recent drips shall be displayed at the top.}.
@@@ A drip shall include the drip text and the date and time that the drip was created.
@@@@ If the drip is not anonymous, the name of the drip's author shall be displayed with the drip text.
@@@ If no drip belongs in the drip list as per Section~\ref{drip-list-belonging}, the page shall display the following message: ``This bucket has no drips.''

\end{easylist}
\end{document}