\documentclass{article}
\usepackage[at]{easylist}
\usepackage[margin=1in]{geometry}

\begin{document}

\section*{Detailed Requirements (revised version)}

\begin{easylist}[articletoc]
@ When the user clicks a bucket name in the bucket list, the user shall be directed to said bucket's page. This bucket name shall hereafter be referred to as the \textit{bucket name}, and this page shall hereafter be referred to as the \textit{bucket page}.
@@ The bucket page shall display a \textit{back button} labeled ``Back'' at the top of the page.
@@@ When the user clicks the back button, the user shall be directed to the home page.
@@ The bucket page shall display a \textit{bucket title} immediately below the back button.
@@@ The text of the bucket title shall be ``$\ll$bucket name$\gg$ Bucket.''
@@ The bucket page shall display a \textit{drip list} immediately below the bucket title.
@@@ \label{drip-list-belonging}A drip shall belong in the drip list if said drip's \texttt{bucketNames} array contains the bucket name. This containment check shall be performed in a case-sensitive manner.
@@@ Drips belonging in the drip list as per Section~\ref{drip-list-belonging} shall be listed in reverse chronological order\footnote{That is, the more recent drips shall be displayed at the top.}.
@@@ A drip shall include the drip text and the date and time that the drip was created.
@@@@ If the drip is not anonymous, the name of the drip's author shall be displayed with the drip text.
@@@ If no drip belongs in the drip list as per Section~\ref{drip-list-belonging}, the page shall display the following message: ``This bucket has no drips.''
@ The user will have an option of choosing whether the drips will show the username while being displayed in the respective bucket page(s), or not.
@@ The user can choose anonymity while creating a new drip by checking the checkbox labeled \textit{Make Anonymous}.
@@@ The \textit{Make Anonymous} checkbox will be unchecked by default.
@@ The \texttt{Drip} model shall have a field named \texttt{anonymous} of data type \texttt{Boolean}.
@@@ If a drip is anonymous, the drip's \texttt{anonymous} field shall be set to \texttt{true}; otherwise, the \texttt{anonymous} field shall be set to \texttt{false}.
@@ An anonymous drip shall not have any username displayed when viewed in its respective bucket page(s).
@@ An anonymous drip will still be associated with its respective username in the database but will not show the username in the bucket page.
@ The user will have the option to logout of the webpage via a \textit{logout button}.
@@ When the user clicks the \textit{logout button}, the user will be directed to the \textit{intro page}.
@@ The \textit{logout button} will be visable at the top of the page on the \textit{home page} and also the \textit{bucket page}.

\end{easylist}
\end{document}
